### 2022-10-02 manuscript/manuscript.tex
more writing

Much work has been done on developing mathematical theory for two primary
selection processes: hitchhiking and background selection. In turn, statistical
methods have use this theory for a variety of wide-ranging empirical problems.
Early on, researchers found correlations between recombination rates and
genetic diversity in small genomes with limited recombination like
\emph{Drosophila} (XXX), consistent with linked selection processes acting on
genome-wide scales. With population genomic data, small-scale (XXX kb) dips in
genetic diversity was evidence of rare but strong selective sweeps in humans
(XXX) and other species (XXX).

models of background selection can
closely predict levels of human-chimp divergence at the megabase scale (XXX).

humans (XXX), though these offered only a partial picture of the selection
processes acting (XXX).

Linked
selection studies have found additional strong selective sweeps in taxa across
the kingdom of life (XXX), and attention turned towards estimating the relative
contributions of the hitchhiking and background processes (Eyalshiv).
processes (Eyalshiv).

From an evolutionary perspective, models of linked selection

@@

>>>>

Much work has been done on developing mathematical theory for two primary
selection processes: hitchhiking (linked selection due to beneficial alleles
increasing in frequency) and background selection (linked selection due to the
selection against deleterious alleles). In turn, statistical methods have use
this theory for a variety of wide-ranging empirical problems. Early on,
researchers found correlations between recombination rates and genetic
diversity in organisms with limited recombination like \emph{Drosophila} (XXX),
consistent with linked selection processes acting on genome-wide scales. With
population genomic data, evidence of small-scale (XXX kb) dips in genetic
diversity was found, caused by rare but strong selective sweeps in humans (XXX)
and other species (XXX). Remarkably, a simple mathematical model of background
selection could closely predict levels of human-chimp divergence at the
megabase scale (XXX) from genome-wide patterns of recombination and regions
conserved between species (McVicker). Another central empirical goal is to
disentangle the relative effect of the these two selection processes on levels
of genetic diversity (Eyalshiv).

Additionally, linked selection can impact other evolutionary processes in two
critical ways. First, while most evolutionary models consider genetic drift to
be the main source of random fluctuations in neutral allele frequencies, linked
selection has a similar impact on neutral sites, increasing the variance in
allele frequency change as if the population size were effectively smaller.
Second, by perturbing the frequencies of neighboring alleles, selection can
interfere with their selection dynamics, known as Hill-Robertson interference
(XXX).

even when sites under selection are sparse.

From an evolutionary perspective, linked selection is important because by
modifying neighboring levels of genetic diversity, it is also directly altering
the selection dynamics at these neighboring sites.

Typically evolutionary genetic models consider

This is known as selective interes

@@

XXX how many sites are under selection at any moment? What's fitness variation?
